Figures

### 2019-06-17 figures/09_stream_buffer.Rmd
turn on cowplot theme

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```

>>>>

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
  theme_cowplot() +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```
